# Set up a project

First, choose _New Project_ and _New Directiory_. 

Second, choose _Book Project using bookdown_ and pick a name as well as the directory. RStudio will automatically set up the Rproject as well as the folder skeleton. 

Third, use the package `usethis` and tie the project with Git. It will re-open the existing project with ready Git integration
```{r eval=FALSE}
library(usethis)
use_git()
```

Fourth, use the package `usethis` again and create a GitHub repo if the project name is available on the owner's repos. When facing git protocol, choose `https`. 
```{r eval=FALSE}
> library(usethis)
> use_github()

✔ Setting active project to '/Users/sushicat/Dropbox/R_Me/Bradford'
✔ Checking that current branch is 'master'
Which git protocol to use? (enter 0 to exit) 

1: ssh   <-- presumes that you have set up ssh keys
2: https <-- choose this if you don't have ssh keys (or don't know if you do)

Selection: 2
● Tip: To suppress this menu in future, put
  `options(usethis.protocol = "https")`
  in your script or in a user- or project-level startup file, '.Rprofile'.
  Call `usethis::edit_r_profile()` to open it for editing.
● Check title and description
  Name:        Bradford
  Description: 
Are title and description ok?

1: Not now
2: Nope
3: I agree

Selection: 3
✔ Creating GitHub repository
✔ Setting remote 'origin' to 'https://github.com/dataning/Bradford.git'
✔ Pushing 'master' branch to GitHub and setting remote tracking branch
✔ Opening URL 'https://github.com/dataning/Bradford'
```
